Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
Correcciones, sugerencias y peticiones
@deantares @fergunet Echadle un ojo a los comentarios con la etiqueta
'Antonio', porfa

\documentclass[preprint]{elsarticle}
\biboptions{round, numbers}
\usepackage[latin1]{inputenc}
%\usepackage[T1]{fontenc}
%\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{color}
%\usepackage{setspace}
\usepackage{url}
\usepackage[english]{babel}

@@

%FERGU: HABLANDO DE LOS PRODUCTOS
{\em MobileFirst} \footnote{\url{http://www.ibm.com/mobilefirst}} is a set of mobile applications and services, based in big data analytics and cloud computing. It includes several products, such as a framework for app development (MobileFirst Platform), a Platform as a Service (BlueMix) or a threat detection system (Trusteer Rapport). %FERGU: sí, es rApport, no rEpport, no lo cambiéis :P
 However, the most interesting one with respect to this work scope, is {\em MobileFirst Protect}. This product, formerly known as {\em MaaS360}) \footonote{\url{http://www.maas360.com/}}, is a MDM (Mobile Device Management) software to securize, monitor and manage mobile devices.  It uses a web portal in order to centralize the security and control policies. This allows the deployment of applications or backups, among other possibilities.
%----------------------------------------------------------------------------

@@

WSO2 Enterprise Mobility Manager (WSO2 EMM) \cite{WSO2_tool} is an open source platform that also works with the BYOD program. Some of this WSO2 EMM key features are:

\begin{description}
  \item[Mobile Device Management,] which is used to manage both user and corporate owned devices, providing support for Android and iOS at the moment. It should be noted that this tool allows tracking every enrolled device, as well as obtaining reports and analytics of their use.
  \item[Mobile Application Management:] With regard to the software, this platform is able to allow or deny the use of applications on enrolled devices based on the role of the user or policies, thus restricting the use of some apps to certain users.
  \item[Enterprise App Store:] This store provides users with both enterprise and public applications approved by the company.
  \item[Mobile Data Security:] WSO2 also allows the user's data to be encrypted via password.
\end{description}

@@

Another important fact is that MUSES functionalities are completed by a human controller, normally the CSO, who supervises the system activity by means of a graphic interface the CSO can interact with. Thus, adapted and inferred security rules are not directly added to the current set of rules, but they are proposed instead as draft rules to this human controller, in order to be accepted if they are interesting and useful. The system also uses the acceptance or rejection of new rules as `feedback`, learning from these decisions, and refining the rules according to this.

@@

\item The information about the user behaviour with respect to system messages, whether the users acts in consequence or against MUSES advice, as well as user feedback. The user feedback has been measured in the MUSES trials by making interviews with the people who have used MUSES, but it can also be measured by pop-up messages, ``has this information been useful?''-type. All this information contributes to the inference of new rules or in adaptation, in order to deal with, for instance, users that repeatedly ignored warning messages.
Moreover, important log information with regard to the parameters used or the decisions made in the different modules can be used for further tests of new inferred rules, as it is explained below.

@@

MUSES is mainly a free, open-source, platform independent solution, and adopts the recommended best practices by Romer \cite{Romer14BestPractices}. %Está bien aquí Fergu?
 These features make it a good alternative to most of the proprietary, close and system-specific tools presented in Section \ref{sec:toolsreview} (all but WSO2). In addition, most of the existing tools take into account only smartphones and tablets, but MUSES also covers laptops and company PCs, thus, it is not only for BYOD. Moreover, the companies which might want to work with one of the reviewed systems need a specific operating system in the server (such as Windows Server, for instance), being even more restrictive in some cases. This is specially remarkable in the case of the Blackphone, forcing the companies and the employees to purchase a specific device. MUSES is a good solution towards these cases, since it is a multiplatform system in both the client and the server.

@@

In addition, a scientific comparison between the techniques used in the proposed system and those in the literature, in the same scope, has been done. It has been discussed that MUSES has the advantage of being multiplatform, while most of the reviewed tools are not. In addition, MUSES is able to adapt and evolve the security policies that a company has built, and not only apply them, as the other tools do. Also, it is remarkable that this MUSES tool is not a solution offered by a company, but the result of the effort of going beyond the state of the art in different fields of research.

@@

\section{Acknowledgements}
This paper has been funded in part by European project MUSES
(FP7-318508), along with Spanish National projects
TIN2011-28627-C04-02
(ANYSELF) and TIN2014-56494-C4-3-P (EphemeCH), and GENIL PYR-2014-17,
awarded by the CEI-BioTIC UGR.

>>>>

\documentclass[preprint]{elsarticle}
\biboptions{round, numbers}
\usepackage[latin1]{inputenc}
%\usepackage[T1]{fontenc}
%\usepackage{textcomp}
\usepackage{array,booktabs,graphicx}
\usepackage{color}
%\usepackage{setspace}
\usepackage{url}
\usepackage[english]{babel}

@@

%FERGU: HABLANDO DE LOS PRODUCTOS
{\em MobileFirst} \footnote{\url{http://www.ibm.com/mobilefirst}} is a set of mobile applications and services, based in big data analytics and cloud computing. It includes several products, such as a framework for app development (MobileFirst Platform), a Platform as a Service (BlueMix) or a threat detection system (Trusteer Rapport). %FERGU: sí, es rApport, no rEpport, no lo cambiéis :P
 However, the most interesting one with respect to this work scope, is {\em MobileFirst Protect}. This product, formerly known as {\em MaaS360} \footnote{\url{http://www.maas360.com/}}, is a MDM (Mobile Device Management) software to securize, monitor and manage mobile devices.  It uses a web portal in order to centralize the security and control policies. This allows the deployment of applications or backups, among other possibilities.
%----------------------------------------------------------------------------

@@

WSO2 Enterprise Mobility Manager (WSO2 EMM) \cite{WSO2_tool} is an open source platform that also works with the BYOD program. Some of this WSO2 EMM key features are:
% Antonio - cambio esto porque las negritas no se suelen usar apenas y para mantener la concordancia en formato con el resto de listas
\begin{itemize}
  \item \textit{Mobile Device Management}: Which is used to manage both user and corporate owned devices, providing support for Android and iOS at the moment. It should be noted that this tool allows tracking every enrolled device, as well as obtaining reports and analytics of their use.
  \item \textit{Mobile Application Management}: With regard to the software, this platform is able to allow or deny the use of applications on enrolled devices based on the role of the user or policies, thus restricting the use of some apps to certain users.
  \item \textit{Enterprise App Store}: This store provides users with both enterprise and public applications approved by the company.
  \item \textit{Mobile Data Security}: WSO2 also allows the user's data to be encrypted via password.
\end{itemize}

@@

Another important fact is that MUSES functionalities are completed by a human controller, normally the CSO, who supervises the system activity by means of a graphic interface he/she can interact with. Thus, adapted and inferred security rules are not directly added to the current set of rules, but they are proposed instead as draft rules to this human controller, in order to be accepted if they are interesting and useful. The system also uses the acceptance or rejection of new rules as `feedback`, learning from these decisions, and refining the rules according to this.

@@

\item The information about the user behaviour with respect to system messages, whether the users acts in consequence or against MUSES advice, as well as user feedback. The user feedback has been measured in the MUSES trials by making interviews with the people who have used MUSES, but it can also be measured by pop-up messages, such as ``has this information been useful?''. 
% Antonio - quito el guión porque un revisor dice que se usan demasiados y que hacen el texto menos fluído y legible.
All this information contributes to the inference of new rules or in adaptation, in order to deal with, for instance, users that repeatedly ignored warning messages.
Moreover, important log information with regard to the parameters used or the decisions made in the different modules can be used for further tests of new inferred rules, as it is explained below.

@@

MUSES is mainly a free, open-source, platform independent solution, and adopts the recommended best practices by Romer \cite{Romer14BestPractices}. %Está bien aquí Fergu?
These features make it a good alternative to most of the proprietary, close and system-specific tools presented in Section \ref{sec:toolsreview} (all but WSO2). In addition, most of the existing tools take into account only smartphones and tablets, but MUSES also covers laptops and company PCs, thus, it is not only for BYOD. Moreover, the companies which might want to work with one of the reviewed systems need a specific operating system in the server (such as Windows Server, for instance), being even more restrictive in some cases. This is specially remarkable in the case of the Blackphone, forcing the companies and the employees to purchase a specific device. MUSES is a good solution towards these cases, since it is a multiplatform system in both the client and the server. 
Table \ref{tab:comparison} summarizes the features of the main analyzed tools, regarding these facts.
% Antonio - Antares, ¿podrías incluir en la comparativa las otras herramientas que se han analizado? Las de Citrix, WSO2, Azzurri, Good...

\begin{table}[ht]

  \centering
  \renewcommand{\arraystretch}{1.5}% Spread rows out...
%  \resizebox{8cm}{!}{
  \begin{tabular}{>{\centering\bfseries}m{1in} >{\centering}m{1in} >{\centering}m{1in} >{\centering\arraybackslash}m{1in}}
    \toprule
      & \textbf{License} & \textbf{Devices} & \textbf{Price} \\
    \midrule
    MUSES & Open Source & IOS, Android, Windows Phone & Free  \\
    IBM Mobile Security & Proprietary &  &  \\
    Sophos Mobile Control & Proprietary & IOS, Android, Windows Phone  &  By Request\\
    Samsung Knox and Blackbery Balance & Proprietary & IOS, Android, Samsung Devices & 12\$ per year/device \\
    Blackphone & Proprietary & Own device & 120\$ per year \\
    Android for Work & Proprietary & Android and devices with Chrome Browser &  12\$ per month/user\\
    \bottomrule
  \end{tabular}
%  }
  \caption{Features of the analyzed products considering licenses, type of devices and price. \label{tab:comparison}}
\end{table}
% Antonio - Antares, ¿no había más tablas?
% Por favor, que alguien rellene los datos de la solución de IBM. ¿Fergu?¿Antares?
% Quizá habría que indicar que MUSES se puede instalar en PC también en la tabla. ¿Sabéis si los demás se puede o son sólo para smartphones/tablets?

@@

In addition, a comparison between the techniques used in the proposed system and those in the literature, in the same scope, has been done. It has been concluded that the biggest advantage of MUSES with respect to the rest is its ability to adapt and evolve the security policies (security rules) that a company has built, and not only apply them, as the other tools do. 
% Antonio - pongo primero la adaptabilidad del sistema porque es la característica más relevante y más 'científica'
Moreover it has the advantage of being multiplatform, while most of the reviewed tools are not.
Also, it is remarkable that this MUSES tool is not a solution offered by a company, but the result of the effort of going beyond the state of the art in different fields of research in corporate security, such as risk and trust analysis or event correlation.

@@

\section{Acknowledgements}
This paper has been funded in part by European project MUSES
(FP7-318508), along with Spanish National projects
TIN2011-28627-C04-02 (ANYSELF) and TIN2014-56494-C4-3-P (EphemeCH), along with GENIL PYR-2014-17, awarded by the CEI-BioTIC UGR.

### 2015-07-08 table_License_Devices_price.tex
Correcciones, sugerencias y peticiones
@deantares @fergunet Echadle un ojo a los comentarios con la etiqueta
'Antonio', porfa

  \centering
  \caption{License, Devices and plataform and prices}
  \renewcommand{\arraystretch}{1.5}% Spread rows out...
  \resizebox{8cm}{!}{
  \begin{tabular}{>{\centering\bfseries}m{1in} >{\centering}m{1in} >{\centering}m{1in} >{\centering\arraybackslash}m{1in}}
    \toprule
      & \textbf{License} & \textbf{Devices} & \textbf{Price} \\
    \midrule
    MUSES & OpenSource &  & Free*  \\
    IBM Mobile Security & Propietary &  &  \\
    Sophos Mobile Control & Propietary & IOS, Android, Windows Phone  &  By Request\\
    Samsung Knox and Blackbery Balance & Propietary & Android Samsung Devices and IOS & 12\$ per year/device \\
    Blackphone & Propietary & Own device & 120\$ per year \\
    Android for Work & Propietary & Android and devices with Chrome Browser &  12\$ per month/user\\
    \bottomrule
  \end{tabular}
  }
\end{table}

>>>>

  \centering
  \renewcommand{\arraystretch}{1.5}% Spread rows out...
%  \resizebox{8cm}{!}{
  \begin{tabular}{>{\centering\bfseries}m{1in} >{\centering}m{1in} >{\centering}m{1in} >{\centering\arraybackslash}m{1in}}
    \toprule
      & \textbf{License} & \textbf{Devices} & \textbf{Price} \\
    \midrule
    MUSES & OpenSource &  & Free*  \\
    IBM Mobile Security & Proprietary &  &  \\
    Sophos Mobile Control & Proprietary & IOS, Android, Windows Phone  &  By Request\\
    Samsung Knox and Blackbery Balance & Proprietary & Android Samsung Devices and IOS & 12\$ per year/device \\
    Blackphone & Proprietary & Own device & 120\$ per year \\
    Android for Work & Proprietary & Android and devices with Chrome Browser &  12\$ per month/user\\
    \bottomrule
  \end{tabular}
%  }
  \caption{Features of the analyzed products considering licenses, type of devices and price.}
\end{table}
